Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation

### 2020-02-24 analysis/paper.Rmd
Added a conclusion and made a few style edits

In this work, we are attempting to confirm that the underlying data provided is the same as that used in the original study by replicating the figure showing the pair-wise correlation of all lance dimensions across the three underlying datasets (original study Fig 8). We are also attempting to replicate the original finding that there was found to be an association between overall centroid size and shape that could not be expained through site difference via an ANOVA analysis.

@@

@@

>>>>

In this work, we are attempting to confirm that the underlying data provided is the same as that used in the original study by replicating the figure showing the pair-wise correlation of all lance dimensions across the three underlying datasets (original study Fig 8). We are also attempting to replicate the original finding that there was found to be an association between overall centroid size and shape that could not be explained through site difference via an ANOVA analysis.

@@

Our attempt at a replication of two parts of the paper _Shape as a measure of weapon standardization: From metric to geometric morphometric analysis of the Iron Age ‘Havor’ lance from Southern Scandinavia_ by Birch and Martinon-Torres was an overall success despite some missing documentation and inconsistencies between the paper and provided code.

Specifically, the replication attempt of the figure showing the pair-wise correlation of all lance dimensions across the three underlying datasets (original study Fig 8) was used to confirm that the underlying data provided by the authors was the same as that used in the analysis. This replication attempt was complicated by the lack of the code used to generate the plot in the provided R file. Additionally, the correlation coefficients noted in the R file comments did not match the figure in the original paper. We were able to create a similar figure to the one in the original paper; but without a clear expected outcome, we were unable to confirm that the provided dataset was the same one used in the analysis.

The second part of the original paper we attempted to replicate was the original finding that there was found to be an association between overall centroid size and shape that could not be explained through site difference via an ANOVA analysis. The code used to perform this analysis was included in the R file, and the expected results noted in the comments matched the original paper. This made it much easier to evaluate the accuracy of our replication. We ran the same analysis as noted in the provided R code and obtained the same results.

The combination of these two replication efforts combined to make this a successful replication attempt. Although our initial attempt cast doubt on the underlying data, the fact that the second replication matched the expected result suggests that the problem with the first attempt was a transcription error between code and paper and not an indication of bad underlying data.

@@

<What do we put in here???>
